### 2015-07-05 narrative/qos.tex
more edits on qos.

\subsubsection{Resource Management}
Sirocco currently offers automatic resource management capabilities. However,
these features are strictly driven on resource capacity and data resilience
requirements. For this project, we seek to expand the resource management
capabilities to support additional metrics to guide resource management
decisions. Our basic goal is to offer data-centric metrics that help guide the
forced resource management decisions.

\subsubsection{QoS}

\paragraph{Background:} One of the key differentiating features this project offers is driving storage
decisions through quality of service (QoS) \emph{reservations} rather than continuing the current model
of allowing applications to compete, without restriction, for part or all of the storage
resources. This traditional approach leads to intereference
effects~\cite{lofstead:2010:adaptive,liu_hotstorage} that can greatly impact IO performance
predictability. 
%Further, with the introduction of additional tiers in the
%storage stack, the performance variability will increase with greater
%competiion for limited high performance resources. 
%% Temporaily commented out the above sentence, because it may not be true for the next DOE systems. 
Unfettered, this competition will yield lower performance for all users than if applications
attempt to reserve performance, thereby enabling the storage system
to reason over its performance in terms of reservations and actual
performance, accepting reservations that are within resource
availability, rejecting those that would lead to overload.

{\bf {\color{red}Will connect to text on policies. Gary}}

It is important to note that we use performance reservations to
reduce interference and to avoid overload conditions. If the system
uses reservations intelligently, its performance is predictable and
efficient because resources are not wasted on interference. However,
in cases where an appication arrives that needs to run more urgently
than any of the other already running applications, administrators
can rapidly respond to it by reducing the amount of resources taken 
by less urgent applications, allowing the urgent application to finish,
and reverting back to the previous committed resource level.

@@

>>>>

\paragraph{Background:} One of the key differentiating features this project offers is driving storage
decisions through quality of service (QoS) \emph{reservations}, rather than continuing the current model
of allowing applications to compete freely without restriction, for part or all of the storage
resources. This traditional approach leads to intereference effects
\cite{lofstead:2010:adaptive,liu_hotstorage} that can greatly impact IO performance predictability. 
%Further, with the introduction of additional tiers in the
%storage stack, the performance variability will increase with greater
%competiion for limited high performance resources. 
%% Temporaily commented out the above sentence, because it may not be true for the next DOE systems. 
Unfettered, this competition can yield a lower system and application performance 
than the case where applications attempt to reserve storage resources, thereby enabling the storage system
to reason over its performance in terms of reservations and actual
performance, accepting reservations that are within resource
availability and don't violate user or system policies.

{\bf {\color{red}Will connect to text on policies- Gary}}

It is important to note that we use performance reservations to
reduce interference and to avoid overload conditions. If the system
uses reservations intelligently, its performance is predictable and
efficient because resources are not wasted on interference. However,
in cases where an appication arrives that needs to run more urgently
than any of the other already running applications, the system
can rapidly respond to it by reducing the amount of resources taken 
by less urgent applications, allowing the urgent application to finish,
and reverting back to the previous committed resource level. This can
be automatically enforced via user- (or adiminstrator-) specified \textit{policies}
(section \ref{}).

@@

\subsubsection{Resource Management}
{\bf {\color{red} This section will be merged into the QoS - Gary}}
Sirocco currently offers automatic resource management capabilities. However,
these features are strictly driven on resource capacity and data resilience
requirements. For this project, we seek to expand the resource management
capabilities to support additional metrics to guide resource management
decisions. Our basic goal is to offer data-centric metrics that help guide the
forced resource management decisions.
